---
title: "MGARCH Model Evaluation and Selection"
output: html_document
date: "2025-04-26"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Packages
```{r}
#install.packages("rugarch, rmgarch, xts, quantmod")
```

Read Data (N = 37)
```{r}
library(xts)
index_return <- read.csv("Log return Stock Index Data (USD).csv", header = TRUE)
index_return$Name <- as.Date(index_return$Name, format = "%d/%m/%Y")
index_return <- as.xts(index_return)
#dim(index_return)
```

Training and Test Data
```{r}
index_return_train_and_test <- index_return[c(2610:6586),] #Jan 2010 (3977 data)
index_return_train <- index_return[c(2610:5479),] #Jan 2010 - Dec 2020 (2870 data)
index_return_test <- index_return[c(5480:6586),] #Jan 2021 - Mar 2025 (1107 data)
```

ACF, PACF, and Time Series
```{r}
#S&P 500 (US)
#png("S&P 500 (US).png", width = 900, height = 300)  # Width and height in pixels
par(mfrow = c(1, 3))
plot(index_return_train_and_test[,1], line = "l", main = "")
acf(index_return_train_and_test[,1], main = "S&P 500 (US)")
pacf(index_return_train_and_test[,1], main = "")
```
```{r}
#FTSE ADX General (UAE)
#png("FTSE ADX General (UAE).png", width = 900, height = 300)  # Width and height in pixels
par(mfrow = c(1, 3))
plot(index_return_train_and_test[,28], line = "l", main = "")
acf(index_return_train_and_test[,28], main = "FTSE ADX General (UAE)")
pacf(index_return_train_and_test[,28], main = "")
```
```{r}
#OMX Iceland All Share (Iceland)
#png("OMX Iceland All Share (Iceland).png", width = 900, height = 300)  # Width and height in pixels
par(mfrow = c(1, 3))
plot(index_return_train_and_test[,36], line = "l", main = "")
acf(index_return_train_and_test[,36], main = "OMX Iceland All Share (Iceland)")
pacf(index_return_train_and_test[,36], main = "")
```
```{r}
#png("US UAE and Iceland.png", width = 900, height = 600)  # Width and height in pixels
par(mfrow = c(3, 3))
plot(index_return_train_and_test[,1], line = "l", main = "")
acf(index_return_train_and_test[,1], main = "S&P 500 (US)")
pacf(index_return_train_and_test[,1], main = "")
plot(index_return_train_and_test[,28], line = "l", main = "")
acf(index_return_train_and_test[,28], main = "FTSE ADX General (UAE)")
pacf(index_return_train_and_test[,28], main = "")
plot(index_return_train_and_test[,36], line = "l", main = "")
acf(index_return_train_and_test[,36], main = "OMX Iceland All Share (Iceland)")
pacf(index_return_train_and_test[,36], main = "")
```


DCC-GARCH (Model Testing), also CCC-GARCH (dccOrder = c(0,0))
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0,0)),
                                              distribution.model = "std"))) #specifies ARMA(0,0)-GARCH(1,1) model, and replicate 37 times
#distribution.model = "std" for student t

#estimate univatiate GARCH models using 'multifit'
#multf <- multifit(uspec.n, index_return_train_and_test) #estimated parameters of all 37 univariate GARCH models

#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "DCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#estimate the DCC-GARCH model
dccfit <- dccfit(spec1, data = index_return_train_and_test, out.sample = 1107, 
                 fit.control = list(eval.se = FALSE),  
                 solver = "solnp") #list(eval.se = TRUE) produces estimated errors for estimated parameters
#fit = multf
dccfit
```

Covariance and corrrelation matrix
```{r}
#fit images
plot(dccfit)

#covariance and correlation matrix
cov_dcc <- rcov(dccfit)
cor_dcc <- rcor(dccfit)

#last day correlation matrix
#cor_dcc[, , dim(cor_dcc)[3]]
```
```{r}
#cov_dcc[[2870]]
```

Plotting Squared Residuals and Estimated Conditional Variance
```{r}
png("Volatility Model.png", width = 900, height = 200)  # Width and height in pixels
par(mfrow = c(1, 3))
plot((dccfit@model$residuals[,1])^2, type = "l",
     ylab = "residuals and fitted sigma",
     main = "S&P 500 (United States)")
lines((dccfit@model$sigma[,1])^2, col = "green")
plot((dccfit@model$residuals[,1])^2, type = "l",
     ylab = "residuals and fitted sigma",
     main = "FTSE ADX General (UAE)")
lines((dccfit@model$sigma[,28])^2, col = "orange")
plot((dccfit@model$residuals[,28])^2, type = "l",
     ylab = "residuals and fitted sigma",
     main = "OMX Iceland All Share (Iceland)")
lines((dccfit@model$sigma[,36])^2, col = "red")
```
```{r}
#CSI 300 (CHINA)
plot((dccfit@model$residuals[,10])^2, type = "l")
lines((dccfit@model$sigma[,10])^2, col = "green")
```
```{r}
#S&P/ASX 200 (AUS)
plot((dccfit@model$residuals[,11])^2, type = "l")
lines((dccfit@model$sigma[,11])^2, col = "green")
```

```{r}
#plot time-varying correlation between index 1 and 2
cor_1_2 <- cor_dcc[2, 1, ]
cor_1_2 <- as.xts(cor_1_2)
plot(cor_1_2)
```
```{r}
#forecast for covariance (rolling does not refit data) (no forecast for CC)
test <- c()
f_dcc <- dccforecast(dccfit, n.ahead = 1, n.roll = 1) #1 step forecast with rolling forecast up to second-last day of 31/3/2025
fcov_dcc <- f_dcc@mforecast$H #1 step forecast covariance matrix
freturn_dcc <- f_dcc@mforecast$mu #1 step forecast conditional return

for (i in 1:2) {
  test <- append(test,list(freturn_dcc[, , i]))
}
test[[2]]
```
```{r}
cov_dcc[, , 2]
```



PCA GARCH (Model Testing)
```{r}
library(rugarch)
library(rmgarch)
library(xts)
library(stats)
```
```{r try 3-5 Principle Components}
#Constructing Principle Components
pca_train <- prcomp(index_return_train, scale = FALSE)
summary(pca_train)
eigen(cov(index_return_train))$values #lambda
```

```{r}
#Scree Plot
plot(pca_train, type = "lines", main = "Scree Plot World Indicies Training Data")
```
```{r}
#Principle Components
pcs <- as.xts(pca_train$x[ ,1:9])
pc1 <- as.xts(pca_train$x[ ,1])
pc2 <- as.xts(pca_train$x[ ,2])
pc3 <- as.xts(pca_train$x[ ,3])
pc4 <- as.xts(pca_train$x[ ,4])
pc5 <- as.xts(pca_train$x[ ,5])

png("PCs.png", width = 900, height = 600)  # Width and height in pixels
par(mfrow = c(3, 3))
plot(pcs[ ,1], line = "l", main = "")
acf(pcs[ ,1], main = "PC1")
pacf(pcs[ ,1], main = "")
plot(pcs[ ,2], line = "l", main = "")
acf(pcs[ ,2], main = "PC2")
pacf(pcs[ ,2], main = "")
plot(pcs[ ,3], line = "l", main = "")
acf(pcs[ ,3], main = "PC3")
pacf(pcs[ ,3], main = "")
```
```{r}
#for analysis
pca.spec.1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 1), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(1, 1), include.mean = FALSE),
                                              distribution.model = "std")
pca1_fit <- ugarchfit(pca.spec.1, data = pcs[ ,1],  
                      solver = "solnp")
pca2_fit <- ugarchfit(pca.spec.1, data = pcs[ ,2],  
                      solver = "solnp")
pca3_fit <- ugarchfit(pca.spec.1, data = pcs[ ,3],  
                      solver = "solnp")
pca4_fit <- ugarchfit(pca.spec.1, data = pcs[ ,4],  
                      solver = "solnp")
pca5_fit <- ugarchfit(pca.spec.1, data = pcs[ ,5],  
                      solver = "solnp")
pca6_fit <- ugarchfit(pca.spec.1, data = pcs[ ,6],  
                      solver = "solnp")
pca7_fit <- ugarchfit(pca.spec.1, data = pcs[ ,7],  
                      solver = "solnp")
pca8_fit <- ugarchfit(pca.spec.1, data = pcs[ ,8],  
                      solver = "solnp")
pca9_fit <- ugarchfit(pca.spec.1, data = pcs[ ,9],  
                      solver = "solnp")
pca1_fit
pca2_fit
pca3_fit
pca4_fit
pca5_fit
pca6_fit
pca7_fit
pca8_fit
pca9_fit
```
```{r}
#plotting squared residuals and estimated conditional variance
plot((pca1_fit@fit$residuals)^2, type = "l")
lines(pca1_fit@fit$var, col = "green")
plot((pca2_fit@fit$residuals)^2, type = "l")
lines(pca2_fit@fit$var, col = "green")
plot((pca3_fit@fit$residuals)^2, type = "l")
lines(pca3_fit@fit$var, col = "green")
```
```{r}
test_cov <- c()
test_ret <- c()
#forecast
pca1_roll_1 <- ugarchforecast(pca1_fit, n.ahead = 1, n.roll = 2)
pca1_roll_2 <- ugarchforecast(pca2_fit, n.ahead = 1, n.roll = 2)
pca1_roll_3 <- ugarchforecast(pca3_fit, n.ahead = 1, n.roll = 2)
  
  #Generate estimated covariance matrix
  for (j in 1:(2 + 1)) {
    L <- pca_train$rotation[ ,1:3]
    sigma_t <- c(pca1_roll_1@forecast$sigmaFor[j],
               pca1_roll_2@forecast$sigmaFor[j],
               pca1_roll_3@forecast$sigmaFor[j])
    D_t2 <- (diag(sigma_t))^2
    V_t <- L %*% D_t2 %*% t(L)
    V_t <- as.matrix(V_t)
    test_cov <- append(test_cov, list(V_t))
  }
test_cov
```








FINAL MODELS

Model 1: AR(1)-DCC-GARCH(1,1)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model1_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                                              mean.model = list(armaOrder = c(1, 0)),
                                              distribution.model = "std"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "DCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for DCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "solnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model1_fcov <- append(model1_fcov, f_dcc_roll@mforecast$H)
}
```

Model 2: MA(1)-DCC-GARCH(1,1)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model2_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                                              mean.model = list(armaOrder = c(0, 1)),
                                              distribution.model = "std"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "DCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for DCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "solnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model2_fcov <- append(model2_fcov, f_dcc_roll@mforecast$H)
}
```

Model 3: DCC-GARCH(1,1) (norm, mvt)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model3_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)), 
                                              mean.model = list(armaOrder = c(0, 0)),
                                              distribution.model = "norm"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "DCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for DCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "solnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model3_fcov <- append(model3_fcov, f_dcc_roll@mforecast$H)
}
```

Model 4: DCC-EGARCH(1,1)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model4_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "eGARCH", garchOrder = c(1, 1)), 
                                              mean.model = list(armaOrder = c(0, 0)),
                                              distribution.model = "std"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "DCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for DCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "gosolnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model4_fcov <- append(model4_fcov, f_dcc_roll@mforecast$H)
}
```

Model 5: aDCC-GARCH(1,1) (norm, mvt)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model5_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0,0)),
                                              distribution.model = "norm"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "aDCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for aDCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "solnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model5_fcov <- append(model5_fcov, f_dcc_roll@mforecast$H)
}
```

Model 6: aDCC-EGARCH(1,1)
```{r}
library(rugarch)
library(rmgarch)
library(xts)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model6_fcov <- c()

#univariate volatility model specification (such that dccfit does not try to fit univariate and multivariate simultaneously)
uspec.n <- multispec(replicate(37, ugarchspec(variance.model = list(model = "eGARCH", garchOrder = c(1, 1)), 
                                              mean.model = list(armaOrder = c(0, 0)),
                                              distribution.model = "std"))) #specifies GARCH(1,1) model, and replicate 37 times
#specifying correlation specifications
spec1 <- dccspec(uspec = uspec.n, dccOrder = c(1, 1), model = "aDCC", distribution = "mvt") #most standard 'dccOrder = c(1, 1)' specification

#loop for DCC model
for (i in 1:refit.num) {
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  dccfit.dummy <- dccfit(spec1, data = index_return_train_and_test, out.sample = out.sample.length, 
                 fit.control = list(eval.se = FALSE),
                 solver = "gosolnp") #list(eval.se = FALSE) to drastically reduce computational time
  f_dcc_roll <- dccforecast(dccfit.dummy, n.ahead = 1, n.roll = n.roll.length)
  model6_fcov <- append(model6_fcov, f_dcc_roll@mforecast$H)
}
```

Model 7: PCA-GARCH(1,1) (norm)
```{r}
library(rugarch)
library(rmgarch)
library(xts)
library(stats)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model7_fcov <- c()

#univariate volatility model specification
pca.spec.1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "norm")
pca.spec.2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "norm")
pca.spec.3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "norm")
#loop for PCA

for (i in 1:refit.num) {
  training_data_size <- 2870 + refit[i]
  testing_data_start <- 2870 + refit[i] + 1
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  
  #Training Data
  pca_train <- prcomp(index_return_train_and_test[1:training_data_size,], scale = FALSE)
  #Obtain Principle Components from Training Data
  pcs_train <- as.xts(pca_train$x[ ,1:3])
  #Use Eigenvectors to obtain PCs for out-of-sample data and combine with training data
  pcs_test <- scale(index_return_train_and_test[testing_data_start:3977, ], center = pca_train$center, scale = pca_train$scale) %*% pca_train$rotation
  pcs_test <- xts(pca_test, order.by = index(index_return_test))
  pcs_train_and_test <- as.xts(rbind(pcs_train, pcs_test[ ,1:3]))
  index(pcs_train_and_test) <- as.Date(index(pcs_train_and_test))
  
  #GARCH Fit and Forecast
  pca1_fit <- ugarchfit(pca.spec.1, data = pcs_train_and_test[ ,1],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca2_fit <- ugarchfit(pca.spec.2, data = pcs_train_and_test[ ,2],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca3_fit <- ugarchfit(pca.spec.3, data = pcs_train_and_test[ ,3],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca1_roll_1 <- ugarchforecast(pca1_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_2 <- ugarchforecast(pca2_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_3 <- ugarchforecast(pca3_fit, n.ahead = 1, n.roll = n.roll.length)
  
  #Generate estimated covariance matrix
  for (j in 1:(n.roll.length + 1)) {
    L <- pca_train$rotation[ ,1:3]
    sigma_t <- c(pca1_roll_1@forecast$sigmaFor[j],
               pca1_roll_2@forecast$sigmaFor[j],
               pca1_roll_3@forecast$sigmaFor[j])
    D_t2 <- (diag(sigma_t))^2
    V_t <- L %*% D_t2 %*% t(L)
    V_t <- as.matrix(V_t)
    model7_fcov <- append(model7_fcov, list(V_t))
  }
}
```

Model 8: PCA-GARCH(1,1) (std)
```{r}
library(rugarch)
library(rmgarch)
library(xts)
library(stats)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model8_fcov <- c()

#univariate volatility model specification
pca.spec.1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
#loop for PCA

for (i in 1:refit.num) {
  training_data_size <- 2870 + refit[i]
  testing_data_start <- 2870 + refit[i] + 1
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  
  #Training Data
  pca_train <- prcomp(index_return_train_and_test[1:training_data_size,], scale = FALSE)
  #Obtain Principle Components from Training Data
  pcs_train <- as.xts(pca_train$x[ ,1:3])
  #Use Eigenvectors to obtain PCs for out-of-sample data and combine with training data
  pcs_test <- scale(index_return_train_and_test[testing_data_start:3977, ], center = pca_train$center, scale = pca_train$scale) %*% pca_train$rotation
  pcs_test <- xts(pca_test, order.by = index(index_return_test))
  pcs_train_and_test <- as.xts(rbind(pcs_train, pcs_test[ ,1:3]))
  index(pcs_train_and_test) <- as.Date(index(pcs_train_and_test))
  
  #GARCH Fit and Forecast
  pca1_fit <- ugarchfit(pca.spec.1, data = pcs_train_and_test[ ,1],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca2_fit <- ugarchfit(pca.spec.2, data = pcs_train_and_test[ ,2],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca3_fit <- ugarchfit(pca.spec.3, data = pcs_train_and_test[ ,3],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca1_roll_1 <- ugarchforecast(pca1_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_2 <- ugarchforecast(pca2_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_3 <- ugarchforecast(pca3_fit, n.ahead = 1, n.roll = n.roll.length)
  
  #Generate estimated covariance matrix
  for (j in 1:(n.roll.length + 1)) {
    L <- pca_train$rotation[ ,1:3]
    sigma_t <- c(pca1_roll_1@forecast$sigmaFor[j],
               pca1_roll_2@forecast$sigmaFor[j],
               pca1_roll_3@forecast$sigmaFor[j])
    D_t2 <- (diag(sigma_t))^2
    V_t <- L %*% D_t2 %*% t(L)
    V_t <- as.matrix(V_t)
    model8_fcov <- append(model8_fcov, list(V_t))
  }
}
```

Model 9: HARMA-PCA-GARCH(1,1) 
```{r}
library(rugarch)
library(rmgarch)
library(xts)
library(stats)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model9_fcov <- c()

#univariate volatility model specification
pca.spec.1 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(1, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.2 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(1, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.3 <- ugarchspec(variance.model = list(model = "sGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
#loop for PCA

for (i in 1:refit.num) {
  training_data_size <- 2870 + refit[i]
  testing_data_start <- 2870 + refit[i] + 1
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  
  #Training Data
  pca_train <- prcomp(index_return_train_and_test[1:training_data_size,], scale = FALSE)
  #Obtain Principle Components from Training Data
  pcs_train <- as.xts(pca_train$x[ ,1:3])
  #Use Eigenvectors to obtain PCs for out-of-sample data and combine with training data
  pcs_test <- scale(index_return_train_and_test[testing_data_start:3977, ], center = pca_train$center, scale = pca_train$scale) %*% pca_train$rotation
  pcs_test <- xts(pca_test, order.by = index(index_return_test))
  pcs_train_and_test <- as.xts(rbind(pcs_train, pcs_test[ ,1:3]))
  index(pcs_train_and_test) <- as.Date(index(pcs_train_and_test))
  
  #GARCH Fit and Forecast
  pca1_fit <- ugarchfit(pca.spec.1, data = pcs_train_and_test[ ,1],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca2_fit <- ugarchfit(pca.spec.2, data = pcs_train_and_test[ ,2],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca3_fit <- ugarchfit(pca.spec.3, data = pcs_train_and_test[ ,3],
                      out.sample = out.sample.length,
                      solver = "solnp")
  pca1_roll_1 <- ugarchforecast(pca1_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_2 <- ugarchforecast(pca2_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_3 <- ugarchforecast(pca3_fit, n.ahead = 1, n.roll = n.roll.length)
  
  #Generate estimated covariance matrix
  for (j in 1:(n.roll.length + 1)) {
    L <- pca_train$rotation[ ,1:3]
    sigma_t <- c(pca1_roll_1@forecast$sigmaFor[j],
               pca1_roll_2@forecast$sigmaFor[j],
               pca1_roll_3@forecast$sigmaFor[j])
    D_t2 <- (diag(sigma_t))^2
    V_t <- L %*% D_t2 %*% t(L)
    V_t <- as.matrix(V_t)
    model9_fcov <- append(model9_fcov, list(V_t))
  }
}
```

Model 10: HARMA-PCA-EGARCH(1,1) 
```{r}
library(rugarch)
library(rmgarch)
library(xts)
library(stats)

#Refit Specifications
refit <- c(0, 100, 200, 300, 400, 500, 600, 700, 800, 900, 1000, 1100, 1107)
refit.num <- length(refit) - 1

#storing rolling covariance matrix
model10_fcov <- c()

#univariate volatility model specification
pca.spec.1 <- ugarchspec(variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(1, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.2 <- ugarchspec(variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(1, 0), include.mean = FALSE),
                                              distribution.model = "std")
pca.spec.3 <- ugarchspec(variance.model = list(model = "eGARCH", garchOrder = c(1, 1)),
                                              mean.model = list(armaOrder = c(0, 0), include.mean = FALSE),
                                              distribution.model = "std")
#loop for PCA

for (i in 1:refit.num) {
  training_data_size <- 2870 + refit[i]
  testing_data_start <- 2870 + refit[i] + 1
  out.sample.length <- 1107 - refit[i]
  n.roll.length <- refit[i+1] - refit[i] - 1
  
  #Training Data
  pca_train <- prcomp(index_return_train_and_test[1:training_data_size,], scale = FALSE)
  #Obtain Principle Components from Training Data
  pcs_train <- as.xts(pca_train$x[ ,1:3])
  #Use Eigenvectors to obtain PCs for out-of-sample data and combine with training data
  pcs_test <- scale(index_return_train_and_test[testing_data_start:3977, ], center = pca_train$center, scale = pca_train$scale) %*% pca_train$rotation
  pcs_test <- xts(pca_test, order.by = index(index_return_test))
  pcs_train_and_test <- as.xts(rbind(pcs_train, pcs_test[ ,1:3]))
  index(pcs_train_and_test) <- as.Date(index(pcs_train_and_test))
  
  #GARCH Fit and Forecast
  pca1_fit <- ugarchfit(pca.spec.1, data = pcs_train_and_test[ ,1],
                      out.sample = out.sample.length,
                      solver = "gosolnp")
  pca2_fit <- ugarchfit(pca.spec.2, data = pcs_train_and_test[ ,2],
                      out.sample = out.sample.length,
                      solver = "gosolnp")
  pca3_fit <- ugarchfit(pca.spec.3, data = pcs_train_and_test[ ,3],
                      out.sample = out.sample.length,
                      solver = "gosolnp")
  pca1_roll_1 <- ugarchforecast(pca1_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_2 <- ugarchforecast(pca2_fit, n.ahead = 1, n.roll = n.roll.length)
  pca1_roll_3 <- ugarchforecast(pca3_fit, n.ahead = 1, n.roll = n.roll.length)
  
  #Generate estimated covariance matrix
  for (j in 1:(n.roll.length + 1)) {
    L <- pca_train$rotation[ ,1:3]
    sigma_t <- c(pca1_roll_1@forecast$sigmaFor[j],
               pca1_roll_2@forecast$sigmaFor[j],
               pca1_roll_3@forecast$sigmaFor[j])
    D_t2 <- (diag(sigma_t))^2
    V_t <- L %*% D_t2 %*% t(L)
    V_t <- as.matrix(V_t)
    model10_fcov <- append(model10_fcov, list(V_t))
  }
}
```

